Data Preparation

### 2019-01-10 Data Preparation.Rmd
Student data, cut explanation
debugging import data - done

## Setup
Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis. The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`. In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
```{r list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')

@@

```{r import data from drive}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
print(d_course)

@@

```{r import d_transcript, cache = TRUE}
d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                     read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
  distinct()
```

>>>>

## Setup
Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis. The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`. In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')

@@

```{r import d_course d_assessment and d_ILO, cache = TRUE}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
print(d_course)

@@

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                      read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
  distinct()
```
